Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
BCP: bad practice -> poor design
BCP: fibonacci -> Fibonacci

This section shows how behaviour driven development works in practice,
by means of the fibonacci function.  Of course this is a very simple
example, but the method is also applicable to more sophisticated
situations where design decisions might not be as obvious as here.

@@

In the next step, we add a specification that forces our function to
actually calculate fibonacci numbers.

@@

So far, so good.  We have an implementaion of the fibonacci function
that swiftly calculates correct values for all positive integers.
But what about negative ones? Our implementation uses the list index
operator {\tt (!!)} which is a partial function that throws an
exeption for negative indexes.  Let's specify that behaviour.

@@

\noindent Throwing exceptions from pure code is considered bad
practice, so we guard the {\tt (!!)} operator against negative
indexes.

>>>>

This section shows how behaviour driven development works in practice,
by means of the Fibonacci function.  Of course this is a very simple
example, but the method is also applicable to more sophisticated
situations where design decisions might not be as obvious as here.

@@

In the next step, we add a specification that forces our function to
actually calculate Fibonacci numbers.

@@

So far, so good.  We have an implementaion of the Fibonacci function
that swiftly calculates correct values for all positive integers.
But what about negative ones? Our implementation uses the list index
operator {\tt (!!)} which is a partial function that throws an
exeption for negative indexes.  Let's specify that behaviour.

@@

\noindent Throwing exceptions from pure code is considered poor
design, so we guard the {\tt (!!)} operator against negative
indexes.
